Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
typos

Since SNOWMED-CT nor ICD cover routine measured activity, we are devising a supplemental ontology for these concepts called \emph{Activity-SENSE}.  This ontology encompasses patient activities, and standard units of measure with which activities are measured, as well as the ability to describe the sensors used.  The intention is for Activity-SENSE records to, like those of SNOMED-CT, eventually be translatable to different languages and mapped to other similiar ontologies of behaviour.

@@

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and of the Web Foundation.  He and Sir Tim Berners-Lee were appointmented as Information Advisors to the UK Government, leading to \url{data.gov.uk}. He is a member of the Public Sector Transparency Board, and Chair of the UK Government’s midata programme.

>>>>

Since SNOWMED-CT nor ICD cover routine measured activity, we are devising a supplemental ontology for these concepts called \emph{Activity-SENSE}.  This ontology encompasses patient activities, and standard units of measure with which activities are measured, as well as the ability to describe the sensors used.  The intention is for Activity-SENSE records to, like those of SNOMED-CT, eventually be translatable to different languages and mapped to other similar ontologies of behaviour.

@@

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and of the Web Foundation.  He and Sir Tim Berners-Lee were appointented as Information Advisors to the UK Government, leading to \url{data.gov.uk}. He is a member of the Public Sector Transparency Board, and Chair of the UK Government's midata programme.
